
% Praneeth Ravuri Resume
% Converted from HTML to LaTeX - Condensed to fit on one page

\documentclass[10pt,a4paper]{article}

% Set custom font size (10.5pt)
\usepackage{anyfontsize}
\renewcommand{\normalsize}{\fontsize{10.75pt}{12.6pt}\selectfont}

% Packages
\usepackage[margin=0.25in]{geometry} % Reduced margins
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage{titlesec}
\usepackage{color}
\usepackage{xcolor}

\definecolor{linkcolor}{rgb}{0,0,1}
\hypersetup{
    colorlinks=true,
    urlcolor=linkcolor,
    linkcolor=linkcolor
}

\setlength{\parindent}{0em}
\setlength{\parskip}{0.3em} % Reduced paragraph spacing

% Section title format with reduced spacing
\titleformat{\section}
{\normalfont\large\bfseries}
{}
{0em}
{}[{\titlerule}]

% Reduce spacing before and after section titles
\titlespacing*{\section}{0pt}{5pt}{3pt}

% Custom commands for header and sections
\newcommand{\dateplace}[2]{\raggedleft #1 \\ #2 \par}
\newcommand{\role}[2]{\raggedright \textbf{#1} \\ #2 \par}

% Reduce itemize spacing
\setlist[itemize]{noitemsep, topsep=0pt, parsep=0pt, partopsep=0pt, leftmargin=*}

\begin{document}

% Header
\begin{center}
    \textbf{\Large Praneeth Ravuri}\\
    \vspace{0.2em}
    571-622-8648 $|$
    \href{mailto:pravdevrav@gmail.com}{ pravdevrav@gmail.com } $|$
    \href{https://praneethravuri.com}{praneethravuri.com} $|$
    \href{https://www.linkedin.com/linkedin.com/prav25}{linkedin.com/linkedin.com/prav25} $|$
    \href{https://www.github.com/github.com/praneethravuri}{github.com/github.com/praneethravuri} $|$
    Richardson, TX
\end{center}
\vspace{-0.3em}

% Education Section
\section*{Education}
\vspace{0.5em}

\begin{minipage}[t]{0.70\textwidth}
    \role{George Mason University}{Master of Science in Computer Science\\Data Analytics, Machine Learning, Distributed Systems}
\end{minipage}
\begin{minipage}[t]{0.29\textwidth}
    \dateplace{Fairfax, VA}{Aug 2022 -- May 2024}
\end{minipage}
\vspace{0.5em}


\begin{minipage}[t]{0.70\textwidth}
    \role{Gokaraju Rangaraju Institute of Engineering & Technology}{Bachelor of Technology in Computer Science\\Cybersecurity, Software Testing, Cloud Computing, Object-Oriented Programming}
\end{minipage}
\begin{minipage}[t]{0.29\textwidth}
    \dateplace{Hyderabad, India}{Jun 2018 -- May 2022}
\end{minipage}
\vspace{0.5em}


% Experience Section
\section*{Experience}
\vspace{0.5em}

\begin{minipage}[t]{0.70\textwidth}
    \role{Prodapt}{Software Engineer}
\end{minipage}
\begin{minipage}[t]{0.29\textwidth}
    \dateplace{Richardson, TX}{Oct 2024 -- Present}
\end{minipage}
\vspace{0em}
\begin{itemize}

    \item Architected high-throughput data pipelines using Golang, processing metrics from 5,000+ devices, enhancing data accuracy and system reliability.
    \item Configured custom decoders for 170+ device metrics, maintaining consistency in network monitoring and improving response time.
    \item Automated error recovery with Python scripts, reducing downtime and preserving data integrity during critical failures.
    \item Developed unit and integration tests to handle 1M+ JSON objects/hour, securing pipeline robustness and reliability.
    \item Optimized database operations with MongoDB and BigQuery, reducing write latency and overhead, improving data processing efficiency.
    \item Streamlined CI/CD workflows using Jenkins, elevating deployment efficiency and cutting manual efforts by 30\%.
\end{itemize}
\vspace{0.5em}


\begin{minipage}[t]{0.70\textwidth}
    \role{Cognizant}{Software Engineer Intern}
\end{minipage}
\begin{minipage}[t]{0.29\textwidth}
    \dateplace{Hyderabad, India}{Jan 2022 -- Jun 2022}
\end{minipage}
\vspace{0em}
\begin{itemize}

    \item Developed a WebSocket-based real-time messaging platform for 500+ users, enabling low-latency communication and improving user engagement.
    \item Enhanced RESTful API performance with Redis caching, achieving message delivery times below 50 ms, significantly boosting application speed.
    \item Containerized and deployed 10 microservices using Docker and Kubernetes, orchestrated through AWS Lambda, enhancing system scalability and reliability.
    \item Collaborated with Agile teams of 12+ members to meet client requirements, delivering projects on tight timelines and ensuring high customer satisfaction.
    \item Integrated OAuth 2.0 for user authentication, reducing unauthorized access attempts and enhancing system security.
\end{itemize}
\vspace{0.5em}


% Skills Section
\section*{Skills}
\vspace{0.5em}
\begin{{itemize}}
    \item \textbf{Programming Languages:} Python, Golang, JavaScript/TypeScript, C/C++, Bash
    \item \textbf{Web Technologies:} React, Next.js, HTML/CSS, Tailwind CSS, FastAPI, Node.js, Express.js
    \item \textbf{Databases:} MySQL, MongoDB, Redis, Pinecone
    \item \textbf{Machine Learning:} Scikit-learn, TensorFlow, PyTorch, Pandas, NumPy, Matplotlib, NLP
    \item \textbf{DevOps and Cloud:} Docker, Kubernetes, Amazon Web Services Lambda, EC2, Jenkins, Vercel, Google Cloud Platform BigQuery, Terraform, Git, GitHub, GitHub Actions
    \item \textbf{Methodologies:} Agile/Scrum, Test-Driven Development (TDD), SDLC
\end{itemize}

% Projects Section
\section*{Projects}
\vspace{0.5em}
\textbf{Retrieval Augmented Generation Document Assistant}
\vspace{{0.5em}}
\begin{{itemize}}
    \item Enhanced document retrieval accuracy by 40\% using a hybrid search RAG system in FastAPI, achieving sub-100 ms query performance.
    \item Constructed 5+ reusable UI components with Next.js, React, and Tailwind CSS, improving user experience and interaction.
    \item Reduced deployment time by 60\% with Docker and automated CI/CD pipelines via GitHub Actions, increasing operational efficiency.
    \item Implemented an IaC solution using Terraform on AWS, provisioning 20 EC2 instances, reducing deployment time by 75\% and ensuring data security.
\end{itemize}
\vspace{{0.5em}}
\textbf{Smart Traffic Management System}
\vspace{{0.5em}}
\begin{{itemize}}
    \item Implemented a reinforcement learning algorithm for traffic light optimization, achieving up to 50\% reduction in vehicle congestion.
    \item Engineered a simulation environment using Python and Pygame, accurately modeling real-world traffic patterns and improving system reliability.
    \item Designed a reward calculation system to evaluate traffic efficiency, enabling optimal decision-making through extensive training iterations.
    \item Conducted comparative analysis of learning parameters, implementing an epsilon decay mechanism for continuous policy enhancement.
\end{itemize}
\vspace{{0.5em}}

\end{document}
